---
title: "Set Up"
output: rmarkdown::github_document

description: >
  Learn how to set up R and RStudio on your machine. We will also demonstrate
  how to install R packages from CRAN, and install the tidyverse package.
---



```{r setup, include=FALSE}
library(learnr)
library(gradethis)
tutorial_options(exercise.timelimit = 60)
```

## Welcome

This is a demo tutorial. Compare it to the [source code](https://github.com/rstudio/learnr/tree/main/inst/tutorials/ex-setup-r/ex-setup-r.Rmd) that made it.

### Outline

This tutorial will help you set up your computer to use R. It is for you if you need to:

* Install R on your computer
* Install the RStudio IDE
* Install the `tidyverse` R package

You can skip this tutorial if you've already done these things.

### Is this tutorial for you?

Do you need to work through the tutorial? Take the quiz below to find out.


```{r quiz1, echo = FALSE}
question("Check all that you have NOT done:",
  answer("installed R on my computer", message = "* Install R"),
  answer("installed the RStudio IDE", message = "* Install RStudio IDE"),
  answer("installed the tidyverse R package", message = "* Install Packages"),
  answer("None of the above. I've done them all.", correct = TRUE, message = "You can skip this tutorial!"),
  type = "multiple",
  incorrect = "This tutorial is here to help! To get set up read:"
)
```

## Install R

### How to install R

![](https://vimeo.com/203516510)

### Test your knowledge

```{r quiz2, echo=FALSE}
quiz(caption = "Quiz - Install R",
  question("Is R free to download and use?",
    answer("Yes!", correct = TRUE, message = "R is free _and_ open source, which means that anyone can read, use, and copy the source code of the R language."),
    answer("No.")
  ),
  question("Where do you download R?",
    answer("www.rstudio.com/download"),
    answer("[cloud.r-project.org](http://cloud.r-project.org)", correct = TRUE, message = "You can also download R from [cran.r-project.org](http://cran.r-project.org)"),
    answer("www.r-project.org", message = "Good try, but not exactly. www.r-project.org doesn't provide a download link, but it does provide a link to one the websites above."),
    answer("www.r.com"),
    allow_retry = TRUE
  ),
  question("How often should you update R?",
    answer("Everytime you use it", message = "This will be too often unless you use R very rarely!"),
    answer("About once a year", correct = TRUE, "A new version of R is released about once a year. Update sooner if you encounter a bug that you cannot explain."),
    answer("Never", message = "A new version of R is released about once a year. I'll assume that you are using the newest version of R, which will be the fastest version with the fewest unexpected behaviors." ),
    allow_retry = TRUE
  )
)
```

## Install RStudio

### How to install RStudio

RStudio is an Integrated Development Environment for R. What does that mean? Well, if you think of R as a language, which it is, you can think of RStudio as a program that helps you write and work in the language. RStudio makes programming in R much easier and I suggest that you use it!

![](https://vimeo.com/203516968)

### Test your knowledge

```{r quiz3, echo=FALSE}
quiz(caption = "Quiz - Install RStudio",
  question("What is the RStudio IDE?",
    answer("An application that makes it easier to use R.", correct = TRUE, message = "RStudio organizes your workspace and makes it easier to write, use, debug, and save R code. I highly recommend it and will rely on the RStudio IDE in several tutorials."),
    answer("An application that let's you use R without writing any code", message = "And thank goodness! Code provides a reproducible record of your work, which is essential for data science."),
    answer("A spreadsheet program like Microsoft Excel."),
    answer("Another name for R", message = "R and RStudio are two separate things. R is a language, like English. Think of RStudio as a program that helps you use the language, kind of like how a word processing program helps you write in English."),
    allow_retry = TRUE
  ),
  question("Is the RStudio IDE free to download and use?",
    answer("Yes!", correct = TRUE, message = "Like R, RStudio is free and open-source. There do exist professional versions of RStudio with enhanced features, but we will not rely on those features in these tutorials."),
    answer("No.", message = "Like R, RStudio is free and open-source. There do exist professional versions of RStudio with enhanced features, but we will not rely on those features in these tutorials.")
  ),
  question("Where do you download RStudio?",
    answer("www.rstudio.com/download", correct = TRUE, message = "For these tutorials, download and install the RStudio Desktop Open Source License."),
    answer("[cloud.r-project.org](http://cloud.r-project.org)", message = "This is where you download R, not RStudio."),
    answer("www.r-project.org"),
    answer("[cran.rstudio.org](http://cran.rstudio.org)"),
    allow_retry = TRUE
  ),
  question("Do you need to install R if you already have RStudio?",
    answer("Yes.", correct = TRUE),
    answer("No.", message = "R does not come with RStudio; you need to install R separately.")
  )
)
```

## Install Packages

### How to install R packages

![](https://vimeo.com/203516241)

### Test your knowledge

```{r names, echo = FALSE}
quiz(caption = "Quiz - Working with Packages",
  question("What command do you use to install packages?",
    answer("`library()`", message = "We will see what `library()` does later."),
    answer("`install.packages()`", correct = TRUE),
    answer("`install_packages()`"),
    answer("There is no command. You must visit [cran.r-project.org](http://cran.r-project.org) and download packages manually.", message = "R makes it easy to download packages. You connect to the internet and then run one of the commands above."),
    allow_retry = TRUE
  ),
  question("How often do you need to install a package on your computer?",
    answer("Every time you restart R"),
    answer("Every time you restart your computer"),
    answer("Only once. Afterwards, R can find it on your hard drive as needed.", correct = TRUE),
    answer("Never, as long as you are connected to the internet.", message = "This could be true if you are using R over a cloud service. However, if you are using R locally on your own computer, you will need to install each package that you use on your computer."),
    allow_retry = TRUE
  ),
  question("What is the tidyverse?",
    answer("A collection of packages that work well together and provide tools for common data science tasks.", correct = TRUE, message = 'You can install all of the tidyverse packages at once with `install.packages("tidyverse")`.'),
    answer("A word processing program for R"),
    answer("A code style that reads like poetry"),
    answer("An alternate universe where everyone is an R programmer."),
    allow_retry = TRUE
  )
)
```


# Write the code

```{r five-power-two, exercise=TRUE}
5^
```

# Write the code 2

```{python five-power-two2, exercise=TRUE}
5**
```



```{r}
grade_this_code()(
  mock_this_exercise(
    .user_code     = "sqrt(log(2))", # user submitted code
    .solution_code = "sqrt(log(1))"  # from -solution chunk
  )
)
#> <gradethis_graded_this_code: [Incorrect]
#>   In `log(2)`, I expected `1` where you wrote `2`. Don't give up now,
#>   try it one more time.
#> >

grade_this_code()(
  mock_this_exercise(
    # user submitted code
    .user_code     = "runif(1, 0, 10)",
    # from -solution chunk
    .solution_code = "runif(n = 1, min = 0, max = 1)"
  )
)
#> <gradethis_graded_this_code: [Incorrect]
#>   In `runif(1, 0, 10)`, I expected `1` where you wrote `10`. Try it
#>   again. Perseverence is the key to success.
#> >

# By default, grade_this_code() informs the user that piped code is unpiped
# when comparing to the solution
grade_this_code()(
  mock_this_exercise(
    # user submitted code
    .user_code     = "storms %>% select(year, month, hour)",
    # from -solution chunk
    .solution_code = "storms %>% select(year, month, day)"
  )
)
#> <gradethis_graded_this_code: [Incorrect]
#>   I see that you are using pipe operators (e.g. %>%), so I want to let
#>   you know that this is how I am interpretting your code before I check
#>   it:
#> 
#>   ```r
#>   select(storms, year, month, hour)
#>   ```
#> 
#>   In `storms %>% select(year, month, hour)`, I expected `day` where you
#>   wrote `hour`. But no need to fret, try it again.
#> >

# By setting `correct` or `incorrect` you can change the default message
grade_this_code(
  correct = "Good work!",
  incorrect = "Not quite. {code_feedback()} {random_encouragement()}"
)(
  mock_this_exercise(
    # user submitted code
    .user_code     = "storms %>% select(year, month, hour)",
    # from -solution chunk
    .solution_code = "storms %>% select(year, month, day)"
  )
)
#> <gradethis_graded_this_code: [Incorrect]
#>   Not quite. In `storms %>% select(year, month, hour)`, I expected
#>   `day` where you wrote `hour`. That's okay: you learn more from
#>   mistakes than successes. Let's do it one more time.
#> >
```


